---
title: "Guide to Knitting PDF's with RMarkdown"
author: "Ross"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# General

# Spacing, Page Breaks, Formatting

In general the document with format each object chronologically. But some chuck options will modify the placement of an plot, table or image.

> Bottom line: Markdown is not LaTeX. It was designed for HTML instead of LaTeX.

(Yihui Xie Explaining Markdown, Pandoc,formattting power on SO )[https://stackoverflow.com/a/17648350/9115822]

## Main lesson
Using captions (`fig.cap`) treats plots, table or images diffrerently and by default places one per page.

See `ex_breaks.pdf` and `ex_no_breaks.pdf` to see the difference.

## Sidenote
There are options to set behaviour but they don't work very well, as they dont seem to be strict.

```{r fig_pos, eval=F}
knitr::opts_chunk$set(fig.pos = "t")
```

Where:

> h , here; t , top; b , bottom; p , page of float

# Margin Control

Latex/Pandoc commands can be used in the first layer of the `yaml`. (First layer meaning the same indentation as `title`, `date`, etc.)

```{r margin, eval=F}
geometry: margin=1.2in
```

# Typeface / Font

This is a tricky one because there isn't `R` and `RMarkdown` specific functions to modify the font...

All indications are that you have to use LaTeX.

```
\renewcommand{\familydefault}{\rmdefault}
```
(Some possibilities)[https://www.sharelatex.com/learn/Font_sizes,_families,_and_styles#Font_families]

# Footnotes and Bibliography

# Page Numbers

By default a `RMarkdown` using the `pdf_document` output with have page numbers. Controlled in `yaml` with LaTeX command:

```
header-includes:
  \pagenumbering{gobble}
```


# Tables

If the data is in a `data.frame`, `df` or `tibble` class object then we can just `print()` the data to get a table.

Using the `kable()` function neatens it up with cell borders etc.


```{r tables}
kableExtra::kable(head(iris))
```

## Captions

Using the `caption` argument for `kable` you can add numbered table captions.

> NOTE: when using captions `kable` rearranges the placing of the table.

<pre><code>```{r cars2, echo=F}
knitr::kable(head(mtcars))
```</code></pre>

vs

<pre><code>```{r cars2, echo=F}
knitr::kable(head(mtcars), caption = "A Caption")
```</code></pre>
